Turbo fast no compromise gravitational wave parameter estimation

### 2023-01-12 src/tex/ms.tex
Slightly modify first paragraph of the introduction.

% Crux of normalizing flow
Normalizing flow is a neural-network based technique that aims at learning a
mapping between a simple distribution, such as a Gaussian distribution, to a
complex distribution, often given in the form of data samples from a target
distribution \cite{2019arXiv190809257K, 2019arXiv191202762P}. Once the network is trained, one can evaluate the probability
density of the complex distribution and samples from it very efficiently.
The core equation of normalizing flow is given by
\begin{align}
    p_x(X) = p_z(Z) \left| \frac{\partial f}{\partial z}\right|,
\end{align}
where $p_x(X)$ is the complex target distribution $p_z(Z)$ is the simple latent
distribution and $f$ is an invertible parameterized transform that
connect the two distributions. For a detailed discussion of the algorithm, we
refer the readers to \kw{cite}.

@@

To demonstrate the performance of our parameter estimation pipeline, we apply
our pipeline to analyze GW150914 and GW170817. The prior used for the two events
are shown in table \ref{tab:parameters}. We use a 4 seconds long segment for the
GW150914 analysis, and a 128 seconds long segment for the GW170817 analysis.
Both data segment are fetched from GWOSC \kw{cite}. Given the specific sampler
setting we use, we produce around an average of 2500 and 3500 \textbf{effective
samples} for GW150914 and GW170817 \footnote{Note that effective sample measures
the number of independent samples, which takes correlation between step into
account, and it is not the same as the number of generated samples. The
effective sample size is computed using
\texttt{arviz},\url{https://python.arviz.org/en/stable/api/generated/arviz.ess.html}.}
in each analysis respectively, which is run on an Nvidia A100 GPU. The
\texttt{wall} time for both event is around 10 minutes. The chain data and the
analysis scripts which generate the chains can be found on
%\kw{\variable{data/} and \variable{script}}
. Most of the time is spent on jit compilation of the code, and the actual
sampling time was about \~150s. Note that we have pre-computed the reference
waveform parameters used in hetetrodyne likelihood for the two events, so the
time spent on solving for the reference waveform parameters is omitted in the
\texttt{wall} time calculation.

@@

% Brief summary
In this work, we present a PE pipeline for GW events that is efficient and
flexible. With differentiable waveform models, heterodyned likelihood and
normalizing flow enhanced sampler \texttt{flowMC}, we can estimate the
parameters of GW150914 and GW170817 in \kw{Quote speed}. Our method is general
and extensible, \kw{continue}.

>>>>

% Crux of normalizing flow
Normalizing flow is a neural-network based technique that aims at learning a
mapping between a simple distribution, such as a Gaussian distribution, to a
complex distribution, often given in the form of data samples from a target
distribution \cite{2019arXiv190809257K, 2019arXiv191202762P}. Once the network is trained, one can evaluate the probability
density of the complex distribution and samples from it very efficiently.
The core equation of normalizing flow is given by
\begin{align}
    p_x(X) = p_z(Z) \left| \frac{\partial f}{\partial z}\right|,
\end{align}
where $p_x(X)$ is the complex target distribution $p_z(Z)$ is the simple latent
distribution and $f$ is an invertible parameterized transform that
connect the two distributions. For a detailed discussion of the algorithm, we
refer the readers to \cite{2019arXiv190809257K, 2019arXiv191202762P}.

@@

To demonstrate the performance of our parameter estimation pipeline, we apply
our pipeline to analyze GW150914 and GW170817. The prior used for the two events
are shown in table \ref{tab:parameters}. We use a 4 seconds long segment for the
GW150914 analysis, and a 128 seconds long segment for the GW170817 analysis.
Both data segment are fetched from GWOSC \kw{cite}. Given the specific sampler
setting we use, we produce around an average of 2500 and 3500 \textbf{effective
samples}\footnote{Note that effective sample measures the number of independent
samples, which takes correlation between step into account, and it is not the
same as the number of generated samples. The effective sample size is computed
using
\texttt{arviz},\url{https://python.arviz.org/en/stable/api/generated/arviz.ess.html}.}
for GW150914 and GW170817 in each analysis respectively, which is run on an
Nvidia A100 GPU. The \texttt{wall} time for both event is around 10 minutes. The
chain data and the analysis scripts which generate the chains can be found on
%\kw{\variable{data/} and \variable{script}}
. Most of the time is spent on jit compilation of the code, and the actual
sampling time was about \~150s. Note that we have pre-computed the reference
waveform parameters used in hetetrodyne likelihood for the two events, so the
time spent on solving for the reference waveform parameters is omitted in the
\texttt{wall} time calculation.

@@

% Brief summary
In this work, we present a PE pipeline for GW events that is efficient and
flexible. Our package put together a number of innovations, including
differentiable waveform models from \texttt{ripple} \kw{cite}, heterodyned
likelihood and normalizing flow enhanced sampler \texttt{flowMC}. We tested the
robustness of our pipeline on a set of 1200 synthetic GW events, showing it is
capable of handling catalog that will be available in the near future. We also
demonstrate our pipeline can estimate the parameters of GW150914 and GW170817 in
\kw{Quote speed}.
